A-maze of Natural Stories: Texts are comprehensible using the Maze task

### 2020-08-25 Papers/Amlap_2020_talk/amlap_2020_talk.tex
draft of talk

\beamertemplatenavigationsymbolsempty 
\setbeamertemplate{mini frames}{}
\setbeamertemplate{itemize item}{\textbullet}

\addtobeamertemplate{navigation symbols}{}{
	\ifnum\insertframenumber>\inserttotalframenumber%
	\relax
	\else%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber
	\fi%
}
\setbeamercolor{footline}{fg=black}
\usepackage{soul}
\makeatletter
\let\HL\hl
\renewcommand\hl{%
	\let\set@color\beamerorig@set@color
	\let\reset@color\beamerorig@reset@color
	\HL}

@@

\title{A-maze: Easier measurement of incremental processing}
\author{Veronica Boyce}
\date{3 June 2020}

@@

\begin{frame}
\maketitle
\end{frame}

%

\section{Why RT?}
\begin{frame}{Why measure reading time?}
\pause
Linguistic and psycholinguistic theories make predictions about processing difficulty.
\medskip
\pause

Examples of increased difficulty
\begin{itemize}\pause
	\item Constructions not in the grammar \pause
	\item Lexical items that are harder to retrieve \pause
	\item Words that force reparsing or reanalysis
\end{itemize}
\pause
\medskip

We assume that harder processing manifests in longer reading/reaction time (RT).
\pause
\medskip

RT patterns may be phenomena that theories need to explain.

@@

\begin{frame}{Two common methods}
%can't get at the internals of processing, so want to use time as proxy for how much is going on 
%but literate humans are good at reading 
\begin{columns}[t]\pause
	\begin{column}{.5\textwidth}
		\begin{center}
			\textbf{\Large Eye-tracking}

			\includegraphics[width=.9\textwidth]{eye-tracker.jpeg}
			\pause
			\begin{itemize}
				\item Expensive
				\item Hard to analyse
			\end{itemize}
		\end{center}
	\end{column}\pause
	\begin{column}{.5\textwidth}
		\begin{center}
\textbf{\Large Self-paced reading}

\begin{tikzpicture} %TODO on slide etc
\draw (-.5,-.5) rectangle (3.2,.5);
\onslide<4>{\node at (0,0) {The};}
\onslide<4>{\node at (1.7,0) {- - - - - - - - - - -};}
\onslide<5>{\node at (0,0) {- - - };}
\onslide<5>{\node at (.7,0) {cat};}
\onslide<5>{\node at (2,0) {- - - - - - - - };}
\onslide<6>{\node at (0.3,0) {- - - - - - };}
\onslide<6>{\node at (1.6,0) {drank};}
\onslide<6>{\node at (2.6,0) {- - - -};}
\onslide<7->{\node at (.9,0) {- - - - - - - - - - -};}
\onslide<7->{\node at (2.7,0) {milk.};}
\end{tikzpicture}
\end{center}
\onslide<8->{
			\begin{itemize}
	\item Lots of spillover
	\item Messy data 
\end{itemize}
}
\end{column}
\end{columns}
\end{frame}

\begin{frame}{A third option: Maze}
\end{frame}
\begin{frame}{Maze Task}
\centering
\tikzset{
	font={\fontsize{14pt}{12}\selectfont}}
\begin{tikzpicture}
\onslide<1->{\node[draw] (a) at (-1,-.5) {e};}
\onslide<1->{\node[draw] (b) at (1,-.5) {i};}
\onslide<1-2>{\node  (c) at (-1,.5) {The};}
\onslide<1-2>{\node  (d) at (1,.5) {x-x-x};}
\onslide<3-4>{\node  (c) at (-1,.5) {upon};}
\onslide<3-4>{\node  (d) at (1,.5) {dog};}
\onslide<5-6>{\node  (c) at (-1,.5) {revise};}
\onslide<5-6>{\node  (d) at (1,.5) {chased};}
\onslide<7-8>{\node  (c) at (-1,.5) {the};}
\onslide<7-8>{\node  (d) at (1,.5) {wish};}
\onslide<9-10>{\node  (c) at (-1,.5) {mitigate.};}
\onslide<9-10>{\node  (d) at (1,.5) {squirrel.};}
\onslide<2,8>{\node[draw, fill=pink!50] at (a) {e};}
\onslide<4,6,10>{\node[draw, fill=pink!50] at (b) {i};}
\end{tikzpicture}
\end{frame}

\begin{frame}{A third option: Maze}
\begin{columns}
	\begin{column}{0.5\textwidth}
		\begin{center}
		\textbf{\large G-maze}
		\includegraphics[clip, trim=9cm 14cm 11cm 1cm,width=.9\textwidth]{gmaze.pdf}
		\end{center}
	\pause
	\end{column}
	\begin{column}{0.5\textwidth} 
		\begin{center}
		\textbf{\large L-maze}
			\includegraphics[clip, trim=9cm 14cm 11cm 1cm,width=.9\textwidth]{lmaze.pdf}
		\end{center}
	\end{column}
\end{columns}

\medskip
\pause
Sentence ends when a mistake is made.
\pause

Central claim: forces extremely incremental processing (no spillover)

\begin{flushright}
	{\small(Forster et al. 2009; Witzel et al. 2012)}
\end{flushright}
\end{frame}

\section{Experiment 1a}
\begin{frame}{Web Implementation}
Maze well suited to run on the web
\begin{itemize}
	\item Implement in Ibex
\end{itemize} 
\pause

Test by replicating Witzel et al. (2012)
\begin{itemize}
	\item Witzel et al (2012): Comparison of eye-tracking, SPR, L-maze, G-maze (all in-lab)
	\item Got materials and data from Witzel
	\item We run SPR, L-maze, and G-maze on MTurk
\end{itemize}
\end{frame}

\begin{frame}{Materials}

\textbf{Relative Clause}

\sethlcolor{green}
\textit{Low:} The son of the \uline{lady} who politely introduced \hl{herself} was popular at the party.
\sethlcolor{pink}

 \textit{High:} The \uline{son} of the lady who politely introduced \hl{himself} was popular at the party.

\textbf{Adverb Clause}

\sethlcolor{green}\textit{Low:} James will fix the car he \uline{drove} \hl{yesterday}, but he will need some help.

\sethlcolor{pink} \textit{High:} James \uline{will fix} the car he drove \hl{tomorrow}, but he will need some help.

\textbf{Sentence v Noun Phrase conjunction}

\sethlcolor{green} \textit{Comma:} The swimmer disappointed her \uline{coach}, and her mother \hl{tried} to console her.

\sethlcolor{pink}
\textit{No comma:} The swimmer disappointed her \uline{coach} and her mother \hl{tried} to console her.
\end{frame}

\begin{frame}{Results}
\begin{small}	
	\sethlcolor{green}
The son of the lady who politely introduced \hl{herself}\sethlcolor{pink} / \hl{himself} was popular at the party.

\end{small}
\includegraphics[width=\textwidth]{g_rel.pdf}
\end{frame}

\begin{frame}{Results}
\begin{small}

\sethlcolor{green}James will fix the car he drove \hl{yesterday}\sethlcolor{pink} / \hl{tomorrow},  but he will need some help.

\end{small}
\includegraphics[width=\textwidth]{g_adv.pdf}
\end{frame}

\begin{frame}{Results}
\begin{small}	
\sethlcolor{green}The swimmer disappointed her coach\hl{,} and her mother \hl{tried} / \sethlcolor{pink}\hl{tried} to console her.
\end{small}
\includegraphics[width=\textwidth]{g_svnp.pdf}
\end{frame}

\begin{frame}{Interim Summary}
\textcolor{PineGreen}{\Large \textbf{Good news:} G-maze works well over the web (better than L-maze or SPR)}

\pause

\bigskip

\textcolor{Red}{\Large \textbf{Bad news:} I do not want to write G-maze materials.}

@@

\section{A-maze}

\begin{frame}{Meanwhile in Natural Language Processing}
\pause
Language models (LMs)
\begin{itemize}
	\item Trained on large corpora to predict the next word
	\item Given a partial sentence, return probabilities of the next word
\end{itemize}
\pause
Surprisal: negative log probability
\begin{itemize}
	\item 2 bits of surprisal = 1/4
	\item 10 bits of surprisal $\approx$ 1/1000 
	\item +1 surprisal = half as likely
\end{itemize}
\pause
\begin{tikzpicture}
\node (A) at (0,0) {"The dog chased ..."};
\node  (B) at (4,0) [draw, minimum width=1.5cm, minimum height=1.5cm, fill=black] {\textcolor{white}{LM}} ;
\draw [->, thick] (A) -- (B); 
\node[align=left] (C) at (7,0) {"the" 1.2 bits \\"a" 3.1 bits\\"cats" 8 bits\\...\\"wish" 25 bits\\...};
\draw [->, thick] (B) -- (C); 
\end{tikzpicture}
\end{frame}

\begin{frame}{Can we use LMs to choose distractors?}

Use high surprisal according to LM as a proxy for bad in context
\medskip

\pause

\begin{itemize}
	\item Model the target sentence word by word \pause
	\item At each position, choose a high surprisal word
\end{itemize}
\medskip
\pause
Want quality control on distractors
\pause
\begin{itemize}
	\item Restrict to a list of possible distractors \pause
	\item Only consider distractors of same length, frequency as target word \pause
	\item Check distractors until we find one with high surprisal
\end{itemize}

\begin{frame}
\centering
\includegraphics[clip, trim=3.25cm 5cm 2.5cm 2.5cm,width=.9\textwidth]{flow_2.pdf}
\end{frame}
\section{Experiment 1b}

\begin{frame}{Does A-maze work? }
\pause
Test it on materials from Witzel et al. (2012)
\medskip

\pause
Try with two pre-trained LSTM models (Gulordava 2018, Jozefowicz 2016)

\begin{frame}{Does A-maze work?  Yes.} \pause
\includegraphics[width=1\textwidth]{a_all.pdf}
\end{frame}

\begin{frame}{Caveats}
A lot of mistakes on the second word of the sentence ("The \ul{dog} ...") \pause
\includegraphics{graph_errors2.pdf} \pause
Bad participants or bad distractors?

Either way, lots of data loss.
\end{frame}

\begin{frame}{Caveats}

{\large Definitely some bad distractors}
\begin{table}

		\begin{tabular}{rlll}
			Prefix & Correct & Distractor & Error Rate \\
			\hline
			\hline
			Gulordava&&&\\
			\hline
			The & niece & cooks & 44\%\\
			The swimmer & disappointed & propositions & 30\%\\
			The & semester & steroids & 29\%\\
			\hline
			\hline
			 Jozefowicz&&&\\
			\hline
			The & husband & authors & 46\%\\
			Jim & listened & survived & 43\%\\
			The & uncle & roads & 42\%\\
			The & knight & saints & 40\%\\
		\end{tabular}
\end{table}

\section{Experiment 2}

\begin{frame}{Potential improvements}

{\large Option 1: Choose better distractors.} \pause
\begin{itemize}
	\item Tweak thresholds of distractor selection. \pause
	\item Could search for optimal thresholds. \pause
	\item Could manually check and fix distractors. 
\end{itemize}

\begin{frame}{Potential improvements}

{\large Option 2: Be forgiving.} \pause
\begin{itemize}
	\item Just don't terminate on mistakes. \pause
	\item Instead have participant correct mistake and continue.
	\end{itemize}
\end{frame}

\begin{frame}{Maze with Error Correction}
\centering
\tikzset{
	font={\fontsize{14pt}{12}\selectfont}}
\begin{tikzpicture}
\onslide<1->{\node[draw] (a) at (-1,-.5) {e};}
\onslide<1->{\node[draw] (b) at (1,-.5) {i};}
\onslide<1-2>{\node  (c) at (-1,.5) {The};}
\onslide<1-2>{\node  (d) at (1,.5) {x-x-x};}
\onslide<3-4>{\node  (c) at (-1,.5) {upon};}
\onslide<3-4>{\node  (d) at (1,.5) {dog};}
\onslide<5-8>{\node  (c) at (-1,.5) {revise};}
\onslide<5-8>{\node  (d) at (1,.5) {chased};}
\onslide<9-10>{\node  (c) at (-1,.5) {the};}
\onslide<9-10>{\node  (d) at (1,.5) {wish};}
\onslide<11-12>{\node  (c) at (-1,.5) {mitigate.};}
\onslide<11-12>{\node  (d) at (1,.5) {squirrel.};}
\onslide<2,6,10>{\node[draw, fill=pink!50] at (a) {e};}
\onslide<4,8,12>{\node[draw, fill=pink!50] at (b) {i};}
\onslide<7,8>{\node[text=red] at (0,-1.5) {\small Incorrect. Please try again.};}
\end{tikzpicture}
\end{frame}

@@

{\large The ``solution'' to our problems!} \pause

\begin{columns}
	\begin{column}{0.3\textwidth}
		\begin{center}
		\includegraphics[clip, trim=9cm 12.5cm 10cm 1cm,width=\textwidth]{maze_diagram.pdf}
		\end{center}

	\end{column} \pause 
	\begin{column}{0.7\textwidth} 
		\begin{center}
			\begin{itemize}
				\item Easily implemented as a toggle in Ibex \pause
				\item Have all the data \pause
				\item Identify bad participants v bad distractors 
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}
\medskip
\pause

Side effect: Can now run multi-sentence items!
\end{frame}

 %TODO: Needs work from here on!

@@

@@

\begin{frame}{Experiment Plan}
Experiment questions:
\begin{itemize}
	\item Will people do this task?
	\item Can participants comprehend the stories?
\end{itemize}

\pause

Checks on RT data
\begin{itemize}
	\item Check if RT is linear in surprisal (Smith \& Levy 2013)
	\item Check for known effects of word length, frequency
	\item Check for spillover effects
\end{itemize}

\begin{frame}{Participant accuracy}
100 participants each read 1 story \pause
\begin{center}
\includegraphics[width=.8\textwidth]{error.pdf}
\end{center}
\end{frame}
\begin{frame}{Comprehension questions}
\begin{center} \pause
\includegraphics[width=.8\textwidth]{comp.pdf}
\end{center}
\end{frame}

\begin{frame}{Surprisal Effects}

Use 3 LMs to estimate surprisal: smoothed 5-gram, Gulordava RNN, Transformer-XL (Gulordava et al. 2018, Dai et al. 2019)
\pause

@@

\begin{frame}{Surprisal Effects}
\includegraphics[width=.9\textwidth]{gam.pdf}	
\end{frame}
\begin{frame}{What about post-mistake data?}
Exclude data from mistakes or the two words after a mistake.

\includegraphics[width=.9\textwidth]{gam2.pdf}	
\end{frame}

\begin{frame}{Summary}
\begin{itemize}\pause
	\item People will read in the Maze task for 15-20 minutes \pause
	\item It's possible to comprehend during Maze \pause
	\item Distractors are generally good enough \pause
	\item Find expected RT patterns \pause
	\item Very little spillover
\end{itemize}
\end{frame}
\section{Conclusion}

@@

\begin{frame}{Matching distractors}
If unspecified: Match by position
\begin{itemize}
	\item The son of the lady who politely introduced \sethlcolor{green} \hl{herself}\sethlcolor{pink} / \hl{himself} was popular at the party.
\end{itemize}
Can specify labels for each word to pair (within item)
\begin{itemize}
	\item The cat who the dog scared hid in a box.\\pre-1 pre-2 who art noun verb main-verb post-1 post-2 post-3
\item The dog who scared the cat sniffed around the couch.\\ pre-1 pre-2 who verb art noun main-verb post-1 post-2 post-3
\end{itemize}
\end{frame}
%back pocket on more on model results??
%do we even need back pockets??

@@

\includegraphics[]{gam3.pdf}	
\end{frame}

>>>>

\beamertemplatenavigationsymbolsempty 
\setbeamertemplate{headline}{}
\setbeamertemplate{itemize item}{\textbullet}

\addtobeamertemplate{navigation symbols}{}{
	\ifnum\insertframenumber>\inserttotalframenumber%
	\relax
	\else%
	\usebeamerfont{footline}%
	\usebeamercolor[fg]{footline}%
	\hspace{1em}%
	\insertframenumber
	\fi%
}
\addtobeamertemplate{frametitle}{\vspace*{.5cm}}{\vspace*{.5cm}}

\setbeamercolor{footline}{fg=black}
\usepackage{soul}
\makeatletter
\let\HL\hl
\renewcommand\hl{%
	\let\set@color\beamerorig@set@color
	\let\reset@color\beamerorig@reset@color
	\HL}

@@

\title{A-maze of Natural Stories: Texts are comprehensible using the Maze task}
\author{Veronica Boyce, Roger Levy}
\date{AMLaP 2020}

@@

\begin{frame}
\maketitle
%TODO maybe put a picture of Roger's face??, at least acknowledge him 
%Pre-amble -- thank Roger, outline with be methods heavy, and then talk about the specific experiment & how it's relevant to how we think about surprisal 
\end{frame}

% But first -- Incremental processing methods

\begin{frame}{Incremental processing methods}
\pause
Goal: Measure processing difficulty

Assumption: Longer RT = more difficulty
\medskip

\pause
\end{frame}

\begin{frame}{Incremental processing methods}
	How to measure RT?

Usual Methods
\begin{columns}[t]\pause
	\begin{column}{.5\textwidth}
		\begin{center}
			\textbf{\Large Eye-tracking}

			\includegraphics[width=.9\textwidth]{../eye-tracker.jpeg}
			\pause
		\end{center}
	\end{column}\pause
	\begin{column}{.5\textwidth}
		\begin{center}
\textbf{\Large Self-paced reading}

\begin{tikzpicture} %TODO on slide etc
\draw (-.5,-.5) rectangle (3.2,.5);
\onslide<4>{\node at (0,0) {The};}
\onslide<4>{\node at (1.7,0) {- - - - - - - - - - -};}
\onslide<5>{\node at (0,0) {- - - };}
\onslide<5>{\node at (.7,0) {cat};}
\onslide<5>{\node at (2,0) {- - - - - - - - };}
\onslide<6>{\node at (0.3,0) {- - - - - - };}
\onslide<6>{\node at (1.6,0) {drank};}
\onslide<6>{\node at (2.6,0) {- - - -};}
\onslide<7->{\node at (.9,0) {- - - - - - - - - - -};}
\onslide<7->{\node at (2.7,0) {milk.};}
\end{tikzpicture}
\end{center}
\onslide<8->{
}
\end{column}
\end{columns}
\bigskip
Different methods have different trade-offs
\end{frame}

\begin{frame}{An alternative: Maze}
%TODO First mentioned, then more elaborated in 2009 paper, has been used ~dozen times 
\centering
\tikzset{
	font={\fontsize{14pt}{12}\selectfont}}
%TODO Maybe update with circles to show the selections. 
\begin{tikzpicture}
\onslide<1-2>{\node  (c) at (-1,.5) {The};}
\onslide<1-2>{\node  (d) at (1,.5) {x-x-x};}
\onslide<3-4>{\node  (c) at (-1,.5) {upon};}
\onslide<3-4>{\node  (d) at (1,.5) {dog};}
\onslide<5-6>{\node  (c) at (-1,.5) {revise};}
\onslide<5-6>{\node  (d) at (1,.5) {chased};}
\onslide<7-8>{\node  (c) at (-1,.5) {the};}
\onslide<7-8>{\node  (d) at (1,.5) {wish};}
\onslide<9-10>{\node  (c) at (-1,.5) {mitigate.};}
\onslide<9-10>{\node  (d) at (1,.5) {squirrel.};}
\onslide<2,8>{\node[ultra thick, draw=blue, ellipse, minimum width=60pt, minimum height= 25pt,align=center] at (c) {};}
\onslide<4,6,10>{\node[ultra thick, draw=blue, ellipse, minimum width=60pt, minimum height= 25pt,
align=center] at (d) {};}
\end{tikzpicture}
\end{frame}

\begin{frame}{An alternative: Maze}
\begin{columns}
	\begin{column}{0.5\textwidth}
		\begin{center}
		\textbf{\large G-maze}
		\includegraphics[clip, trim=9cm 14cm 11cm 1cm,width=.9\textwidth]{../gmaze.pdf}
		\end{center}
	\pause
	\end{column}
	\begin{column}{0.5\textwidth} 
		\begin{center}
		\textbf{\large L-maze}
			\includegraphics[clip, trim=9cm 14cm 11cm 1cm,width=.9\textwidth]{../lmaze.pdf}
		\end{center}
	\end{column}
\end{columns}

\medskip
\pause
Sentence ends if a mistake is made.
\pause

Claim: forces incremental processing (no spillover)

\begin{flushright}
	{\small(Forster et al. 2009; Witzel et al. 2012)}
\end{flushright}
% Compelling results especially for G-maze, but 
% was run in the lab, and generating G-maze materials is a huge amount of work
\end{frame}

\begin{frame}{Using Maze}
Is Maze a viable alternative to web SPR?

Needs:
\begin{itemize}
	\item Run on web 
	\item Easy generation of distractor words
	\item Work for long or multi-sentence items %this part incidentally makes it easy to do exclusions, and might help with data loss, but we'll talk about that later
\end{itemize} 
\pause

@@

\begin{frame}{Run on web}
	%TODO include screenshot
	Wrote an Ibex module
	\begin{itemize}
		\item Based off SPR module
		\item Fits in with existing workflow
	\end{itemize}
 Replicated Witzel et al. (2012) results (see Boyce et al. 2020)
\end{frame}
%
\begin{frame}{Using Maze}
	Is Maze a viable alternative to web SPR?

	Needs:
	\begin{itemize}
		\item Run on web 
		\item Easy generation of distractor words
		\item Work for long or multi-sentence items %this part incidentally makes it easy to do exclusions, and might help with data loss, but we'll talk about that later
	\end{itemize} 
	\pause

\end{frame}
%
\begin{frame}{Generating distractors}
\pause
Task: Given  \textit{The dog chased} Find a word that can't be a continuation.
\begin{itemize}
	\item Tedious (and hard!) to do by hand. 
\end{itemize}

What makes something an unacceptable continuation?
\begin{itemize}
	\item Ungrammatical
	\item ...or otherwise really unlikely 
	\item $\approx$ high surprisal 
\end{itemize}

Can we use Neural Language Models?
\end{frame}
%
\begin{frame}{Can we use LMs?}
Language models (LMs)
\begin{itemize}
	\item Trained on large corpora to predict the next word
	\item Given a partial sentence, return probabilities of the next word
\end{itemize}

LSTM RNNs (ex. Gulordava 2018) show some syntactic knowledge %TODO cite people

Add some controls:
\begin{itemize}
\item Restrict to a list of possible distractors
\item Only consider length, frequency matches
\end{itemize}

\end{frame}
%
\begin{frame}{Can we use LMs to choose distractors?}

Does it work?

Yes, at least well enough.
\begin{itemize}
	\item Sometimes generates plausible distractors.
	\item Overall results comparable with G-maze %TODO citations to me, Sloggett
	%TODO show graph from Boyce et al
\end{itemize} 
\medskip

Parameter-tweaking may help, as would hand-checking. 
\end{frame}
%
\begin{frame}{Using Maze}
	Is Maze a viable alternative to web SPR?

	Needs:
	\begin{itemize}
		\item Run on web %TODO figure out how to make checkmarks again
		\item Easy generation of distractor words 
		\item Work for long or multi-sentence items %this part incidentally makes it easy to do exclusions, and might help with data loss, but we'll talk about that later
	\end{itemize} 
	\pause

\end{frame}
%
%
\begin{frame}{Long items}

Errors terminate sentences. 
Some error rate is inevitable.

Want to run multi-sentence items. 
\begin{itemize}
	\item Treat whole story as a unit: Almost no one makes it to the end.
	\item Treat each sentence as a unit:
	Many participants miss key context. 
\end{itemize}

What if after an error, participants corrected errors and the sentence continued?

\end{frame}
%
\begin{frame}{Maze with Error Correction}
\centering
\tikzset{
	font={\fontsize{14pt}{12}\selectfont}}

\begin{tikzpicture}
\onslide<1-2>{\node  (c) at (-1,.5) {The};}
\onslide<1-2>{\node  (d) at (1,.5) {x-x-x};}
\onslide<3-4>{\node  (c) at (-1,.5) {upon};}
\onslide<3-4>{\node  (d) at (1,.5) {dog};}
\onslide<5-8>{\node  (c) at (-1,.5) {revise};}
\onslide<5-8>{\node  (d) at (1,.5) {chased};}
\onslide<9-10>{\node  (c) at (-1,.5) {the};}
\onslide<9-10>{\node  (d) at (1,.5) {wish};}
\onslide<11-12>{\node  (c) at (-1,.5) {mitigate.};}
\onslide<11-12>{\node  (d) at (1,.5) {squirrel.};}
\onslide<2,6,10>{\node[ultra thick, draw=blue, ellipse, minimum width=60pt, minimum height= 25pt,align=center] at (c) {};}
\onslide<4,8,12>{\node[ultra thick, draw=blue, ellipse, minimum width=60pt, minimum height= 25pt,
	align=center] at (d) {};}
\onslide<7,8>{\node[text=red] at (0,-1.5) {\small Incorrect. Please try again.};}
\end{tikzpicture}

@@

@@

\begin{columns}
	\begin{column}{0.3\textwidth}
		\begin{center}
		\includegraphics[clip, trim=9cm 12.5cm 10cm 1cm,width=\textwidth]{../maze_diagram.pdf}
		\end{center}

	\end{column} \pause 
	\begin{column}{0.7\textwidth} 
		\begin{center}
			Features
			\begin{itemize}
				\item Easily implemented as a toggle in Ibex \pause
				\item Can look at long materials (in principle)
				\item Have all the data \pause
				\item Identify bad participants v bad distractors 
				%easy to weed out participants who aren't paying attention 
				\item Makes it less of a big deal when we have bad distractors
			\end{itemize}
		\end{center}
	\end{column}
\end{columns}
\medskip
\pause

Side effect: Can now run multi-sentence items!
\end{frame}
%
%%So now that I've explained the method, going to switch over to current experiment & what we hoped to get from it
%
\begin{frame}
	Various open questions we want to address -- really test suitability of Maze
	\begin{itemize}
		\item Do people comprehend/remember what they read?
		\item Does this error correction thing work? 
		\item Are people willing to read texts in this way? 
		\item Do we get predictability effects? (Both SPR, eye-tracking show certain surprisal effects, does Maze?)
	\end{itemize}
\end{frame}

@@

%HARD mode

@@

\begin{frame}{Participant accuracy}
100 participants from MTurk each read 1 story (20 minutes) \pause
\begin{center}
\includegraphics[width=.8\textwidth]{../error.pdf}
\end{center}
\end{frame}
\begin{frame}{Comprehension questions}
\begin{center} \pause
\includegraphics[width=.8\textwidth]{../comp.pdf}
\end{center}
% exclusion options: use comprehension checks as participant filter. Here we can use overall accuracy as the "paying attention" filter. Don't have to worry about how to write good comprehension questions. May still need to do RT exclusions for double-presses or getting distracted. 
\end{frame}

\begin{frame}{Surprisal Effects}
%TODO copy from updated abstract
Use 3 LMs to estimate surprisal: smoothed 5-gram, Gulordava RNN, Transformer-XL (Gulordava et al. 2018, Dai et al. 2019)
\pause

%TODO make sure that updated correct gams are used!!!

@@

\begin{frame}
	Implications for surprisal theory -- size of the effects is different
	include effect sizes
	Is it about participant quality?
\end{frame}

\begin{frame}{Surprisal Effects}
\includegraphics[width=.9\textwidth]{../gam.pdf}	
\end{frame}
\begin{frame}{What about post-mistake data?}
Exclude data from mistakes or the two words after a mistake.

\includegraphics[width=.9\textwidth]{../gam2.pdf}	
\end{frame}

\begin{frame}{Summary}
\begin{itemize}\pause
	\item People will read in the Maze task for 15-20 minutes \pause
	\item It's possible to comprehend during Maze \pause
	\item Distractors are generally good enough \pause
	\item Find expected RT patterns \pause
	\item Very little spillover
\end{itemize}
\end{frame}

@@

\begin{frame}{Matching distractors}
If unspecified: Match by position
\begin{itemize}
	\item The son of the lady who politely introduced \sethlcolor{green} \hl{herself}\sethlcolor{pink} / \hl{himself} was popular at the party.
\end{itemize}
Can specify labels for each word to pair (within item)
\begin{itemize}
	\item The cat who the dog scared hid in a box.\\pre-1 pre-2 who art noun verb main-verb post-1 post-2 post-3
\item The dog who scared the cat sniffed around the couch.\\ pre-1 pre-2 who verb art noun main-verb post-1 post-2 post-3
\end{itemize}
\end{frame}
%%back pocket on more on model results??
%%do we even need back pockets??

@@

\includegraphics[]{../gam3.pdf}	
\end{frame}
